\section {Configure Software}
\index{Admin!Software}
A new software type is added using the script 'plm\_add\_software.pl'.

\section {Configure Source}
\index{Admin!Source}
Once a new software is created, a 'source' for the base must be configured in table 'plm\_source'.  There is currently no script to do this, so I will mention here the important database fields.  Multiple sources and source types are possible for one software type.

\begin{itemize}
\item id: Unique integer identifier
\item plm\_software\_id: Relates back to table 'plm\_software' table
\item plm\_source\_type: Currently 'TAR', 'CVS', future 'BK' etc.
\item root\_location: Top URL for web site, for TAR
\item source\_password: Text password for access to Source Control Repository
\item sc\_module: Module name for Source control Repository
\item sc\_branch: Not implemented
\end{itemize}

\section {Configure SourceSync}
\index{Admin!SourceSync}
In order to sync using plm\_source\_sync.pl from an existing repository, at least one entry must be put into table 'plm\_source\_sync'.  The fields in this table are:

\begin{itemize}
\item id: Unique integer identifier
\item plm\_source\_id:  Relates back to table 'plm\_source'
\item search\_location:  Continuation of URL, for source type TAR
\item depth: How many directories to go down, for source type TAR values start at 0
\item wanted\_regex: A regular expression to match while searching
\item not\_wanted\_regex: A regular expression to NOT match while searching(optional)
\item baseline: 'Y' or 'N', is the file a patch or a base 
\item applies\_regex: A regular expression to match name of applies, for patches NOT bases
\item name\_substitution: a full substitution expression s/xxx/yyy/ (optional)
\item descriptor: A phrase that describes this development tree.
\item last\_timestamp: This is the timestamp for the last base item added.
\end{itemize}


For Source Type TAR, use fields id, plm\_source\_id, search\_location, depth, wanted\_regex (optional), not\_wanted\_regex (optional), baseline, applies\_regex, name\_substitution (optional), descriptor.  For Source Type CVS, use fields id, plm\_source\_id, baseline (only 'Y' supported), descriptor, last\_timestamp. 

To test your newly configured sources, you run plm\_source\_sync.pl with the --list\_only option.  It prints out what plm patches it would create.

\section {Configure plm_software_to_command_set}
\index{Admin!SourceSync}
The script plm\_source\_app.pl executes the build and installations scripts.  If none are configured, this script does not return an error.  If you want it to do something the build information must be entered into three tables:  plm\_software\_to\_command\_set, plm\_command\_set and plm\_command.  The fields in this table plm\_software\_to\_command\_set are:

\begin{itemize}
\item id: Unique integer identifier
\item plm\_software\_id:  id from table plm\_software
\item plm\_command\_set\_id:  id from table plm\_command\_set
\item min\_plm\_patch\_id:  lower bound of legitimate rage for this script
\item max\_plm\_patch\_id:  upper bound of legitimate rage for this script
\end{itemize}


Table plm\_command\_set sets up a unique id for the set in table plm\_command:
\begin{itemize}
\item id: Unique integer identifier
\item name:  Brief, user-friendly identifier
\item command\_set\_type: 'build', 'install' or 'validate'.
\end{itemize}

Table plm\_command contains the actual execution sequence and expected results:
\begin{itemize}
\item id: Unique integer identifier
\item plm\_command\_set\_id:  id from table plm\_command\_set
\item command\_order:  Order to execute in.
\item command:  Can be a executable or a script, single or multi-line.
\item command\_type:  'script' or others may be added
\item expected\_result:  For type 'script', this is the return value.
