\subsection{PLM::Object}
The PLM::Object:: module space has the following sub-modules:

\begin{itemize}
\item Patch.pm
\item Source.pm
\item SourceSync.pm
\item SourceSync/Tar.pm
\item SourceSync/Cvs.pm
\end{itemize}

All of the modules in the PLM::Object:: space are children of the PLM::Object object Template.
These are used when we want to store the data, but not use any of the database access 
functionality.
PLM::Object has two attributes 'elementName' and 'data'.  The 'elementName' attribute is 
the type of data contained for administrative reasons.  The 'data' attribute contains a simple 
hash for the 'active' data, which can be accessed through the routines 'getElementValue', 
'setElementValue', and has 'addElement' for initialising hash.  All methods:

\begin{itemize}
\item addElement( <key>, <value> )  initialising hash.
\item getElementValue( <key> )  access data.
\item setElementValue( <key>, <value> )  set data values.
\item getValue( <key> )  access data, wrapper for getElementValue.
\item setValue( <key>, <value> )  set data values, wrapper for setElementValue.
\item loadDataOnly( <ref> ) To copy data from another PLM::Object to this one.
\item getElementName()  Returns elementName attribute value.
\item setElementName( <elementName> )  Sets elementName attribute value.
\end{itemize}


\subsubsection{Patch.pm}
\index{PLM::Object::Patch.pm}
Provides a Patch object.

\begin{verbatim}
new()
\end{verbatim}
\index{PLM::Object::Patch.pm!new()}
Instantiates a new object of type PLM::Object::Patch.

\subsubsection{Source.pm}
\index{PLM::Object::Source.pm}
Provides a Source object.

\begin{verbatim}
new()
\end{verbatim}
\index{PLM::Object::Source.pm!new()}
Instantiates a new object of type PLM::Object::Source

\subsubsection{SourceSync.pm}
\index{PLM::Object::SourceSync.pm}
Provides a SourceSync object.

\begin{verbatim}
new()
\end{verbatim}
\index{PLM::Object::SourceSync.pm!new()}
Instantiates a new object of type PLM::Object::SourceSync.

\subsubsection{PLM::Object::SourceSync::Tar.pm}
\index{SourceSync\/Tar.pm}
Provides an interface to the SourceSync Object for web access.

\begin{verbatim}
fix_name()
\end{verbatim}
\index{PLM::Object::SourceSync::Tar.pm!fix\_name()}
This script is to do the appropriate name fix is one is required, or return the name unedited.

\begin{verbatim}
name_checks()
\end{verbatim}
\index{PLM::Object::SourceSync::Tar.pm!name\_checks()}
Does checks to see if a file is configured to be 'wanted'.

\begin{verbatim}
get_applies_version()
\end{verbatim}
\index{PLM::Object::SourceSync::Tar.pm!get\_applies\_version()}
From a file name returns what patch it should be applied to.

\begin{verbatim}
get_file_type()
\end{verbatim}
\index{PLM::Object::SourceSync::Tar.pm!get\_file\_type()}
From a file name returns the correct file type.

\begin{verbatim}
isa_base()
\end{verbatim}
\index{PLM::Object::SourceSync::Tar.pm!isa\_base()}
From the patch name, returns 'TRUE' if it is a 'base' and 'FALSE' if if applies to something.

\subsubsection{PLM::Object::SourceSync::Cvs.pm}
\index{SourceSync\/Cvs.pm}
Provides an interface to the SourceSync Object for CVS repository access.   These are functions used for getting information about the CVS repository.

\begin{verbatim}
fix_name()
\end{verbatim}
\index{PLM::Object::SourceSync::Cvs.pm!fix\_name()}
This script is to do the appropriate name fix if one is required, or return the name unedited.

\begin{verbatim}
name_checks()
\end{verbatim}
\index{PLM::Object::SourceSync::Cvs.pm!name\_checks()}
Always returns 'TRUE'.

\begin{verbatim}
get_applies_version()
\end{verbatim}
\index{PLM::Object::SourceSync::Cvs.pm!get\_applies\_version()}
From a file name returns what patch it should be applied to.

\begin{verbatim}
get_file_type()
\end{verbatim}
\index{PLM::Object::SourceSync::Cvs.pm!get\_file\_type()}
From a file name returns the correct file type.

\begin{verbatim}
isa_base()
\end{verbatim}
\index{PLM::Object::SourceSync::Cvs.pm!isa\_base()}
From the patch name, returns 'TRUE' if it is a 'base' and 'FALSE' if if applies to something.

